The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-31 paper.tex
update

To evaluate the photon flux at the energy $\epsilon_{1}$ and\
take into account the perspective projection effect,
we integrate the emissivity along line-of-sights from the solar position:
\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
\end{equation}

>>>>

To evaluate the simulated photon flux at the energy $\epsilon_{1}$ and\
take into account the perspective projection effect,
we integrate the emissivity along line-of-sights from the solar position:
\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
\end{equation}
